\begin{fancyquote}
        [\ldots] The Chinaman, like men of other races, insists upon indulging
        in some stimulant or narcotic, and he has chosen opium. He is by no
        means the teetotaller which he is credited to be. Temperance societies
        exist in China. Still the Chinaman generally does not indulge in beer or
        wine --- a great debarrent being the cost when delivered from Europe ---
        and his \textit{samshu}\footnote{\textit{samshu}, mainly known as
        \textit{baiju} to natives (\zhs{白酒} in Chinese), is a traditional
        Chinese spirit that is overwhelmingly strong at approximately 90 percent
        proof \autocite{Antkiewicz:1993}.} is a weakly subterfuge. The vice
        which it pleases him to indulge in is, therefore, opium. We have not yet
        succeeded in introducing temperance, far less abstinence, into England.
        And you may as soon expect the average Briton to give up his beer or
        spirits as the Chinaman his pipe. In neither case can you make man moral
        by Act of Parliament. No reform, I feel certain, is likely to come from
        the mandarinate, who are nearly without exception slaves to the habit,
        while the few free from it are powerless against it. It must come, if
        ever it does, by social reform, from the people themselves. The import
        of Indian opium by our Government is said by the missionaries to create
        a source of considerable difficulty in their relations with the Chinese.
        If not altogether a sincere belief with Chinamen, it is at least a
        highly convenient argument, and much used by them, that we are largely
        responsible for the prevalence of the habit; and not only the officials
        and \textit{literati} [the far-Eastern intelligentsia], but not a few
        foreigners even, have done their best to foster the idea. True or not
        true, the charge is one difficult to meet so long as Government
        preserves its present attitude with regard to Indian opium. Having in
        view the facts brought forward in this letter --- though of opinion that
        the suppression of the Indian opium traffic will not stop nor even
        diminish its use --- I think Government should take steps to discontinue
        it, and replace it by some other means of revenue. It can hardly be
        called a creditable source of revenue. From the practical financial as
        apart from the moral or sentimental aspect, it is advisable to examine
        the question and seek some means of replacing it. If no such steps be
        taken, Government will have lost the opportunity of carrying a measure
        of progress --- an act of self-respect as well as expediency --- for the
        import of Indian opium into China is doomed. [\ldots]
	\begin{flushright}
		\autocite{SpecialCorrespondent:1884}
	\end{flushright}
\end{fancyquote}
