\begin{fancyquote}
	\vspace*{0.5em}
	\articlehead{[\ldots] Britain --- Article III [\ldots]}
	\vspace*{0.5em}
	His Majesty the Emperor of China hereby agrees that the ambassador, minister, or other diplomatic agent, so appointed by Her Majesty the Queen of Great Britain, may reside, with his family and establishment, permanently at the capital, or may visit it occasionally, at the option of the British Government. He shall not be called upon to perform any ceremony derogatory to him as representing the Sovereign of an independent nation on a footing of equality with that of China. On the other hand, he shall use the same forms of ceremony and respect to His Majesty the Emperor as are employed by the ambassadors, ministers, or diplomatic agents of Her Majesty towards the Sovereigns of independent and equal European nations.
	
	It is further agreed, that Her Majesty's Government may acquire at Peking \emph{[Beijing]} a site for building, or may hire houses for the accommodation of Her Majesty's Mission, and that the Chinese Government will assist it in so doing.
	
	Her Majesty's Representative shall be at liberty to choose his own servants and attendants, who shall not be subjected to any kind of molestation whatever.
	
	Any person guilty of disrespect or violence to Her Majesty's Representative, or to any member of his family or establishment, in deed or word, shall be severely punished. 
	\articlehead{[\ldots] Russia --- Article III [\ldots]}
	Henceforward, trade between Russia and China may be carried out not only at the agreed frontier points, but by sea. Russian merchant vessels may enter the following ports: Shanghai, Ningpo, Fuchow-fu, Amoy, Canton, Taiwan-fu (on the Isle of Formosa \emph{[Taiwan, the Republic of China]}), Khioung-Cheou-fu (on the Isle of Hainan).
	\articlehead{[\ldots] France --- Article XIII [\ldots]}
	The Christian religion having as its aim to bring men to virtue, the members of all Christian sects will have full security of their persons, property and religious practices, and effective protection will be given missionaries who peacefully go into the interior of the country, with passports of the kind mentioned in Article VIII. The Chinese Empire will place no barrier in the way of Chinese individuals who decide to embrace the Christian faith and practice, and these individuals will suffer no punishment.

	All that was written and proclaimed against Christianity in the past by the Chinese Government, or approved by it, is completely abrogated, and is now without value in all provinces of the Empire. \emph{\autocite{Chassiron:1861}}
\end{fancyquote}
